---
title: "Introduction to StatComp21041"
author: "Shi Cheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21041}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## background

### SS function  
Focusing on Speech Separation, which is author's research field, it puzzled me that when calculate some index of experiment performance(say, PESQ), there exist two sets of standards in matlab and python.  
Most papers won't declare which algorithm used, and that causes a chaos when I try to compare different models presented in different papers.  
In this sence, it will be convenient for me to write a function to transfer one to the other.   


### k_means function
Speaker Diarization is also an important field in Speech processing. After obtain features vector, we need to start
a cluster step.   
This function give a fast way to complete this job, and you can determine how many clusters you want.



## Function instruction and useage.

### function SS is defined as follows:
type: the type of index to be transformed, it must be \code{"MOS_lqo"} or \code{"PESQ_mos"}, and quotes involved. 
value: the value to be transformance, in can be a number or a vector, but all numbers must be in (1, 4.5).

```{r}
SS <- function(type, value) {
  x <- c("MOS_lqo")
  y <- c("PESQ_mos")
  if(type == x) {
    value_t <- 46607 / 14945 - (2000 * log(1/(value/4 - 999/4000) - 1)) / 2989
    plot(value, value_t, main = "MOS_lqo to PESQ_mos", 
         xlab = "MOS_lqo", xlim = range(value), ylab = "PESQ_mos", ylim = c(0, 5))
    cat("\nMOS_lqo score:", value)
    cat("\nPESQ_mos score:", value_t)
    cat("\nMOS_lqo score:", mean(value))
    cat("\nPESQ_mos score:", mean(value_t))
  }
  else if(type == y){
    value_t <- 0.999 + ( 4.999-0.999 ) / ( 1 + exp(-1.4945*value + 4.6607) )
    plot(value, value_t, main = "PESQ_mos to MOS_lqo", 
         xlab = "PESQ_mos", xlim = range(value), ylab = "MOS_lqo", ylim = c(0, 5))
    cat("\nPESQ_mos score:", value)
    cat("\nMOS_lqo score:", value_t)
    cat("\nPESQ_mos score:", mean(value))
    cat("\nMOS_lqo score:", mean(value_t))
  }
  else{
    print("Unrecognizid type of index")
  }
}
```

and you can simply use it with \code{SS(type, value)}, for example:

```{r}
SS("MOS_lqo",seq(1, 4.5, by=0.1))
```


you will gain the original vector, the transformed, the mean indices value on testset(which is presented in papers)


### function k_cluster is defined as follows:
x: the abscissa of a point  
y: the ordinate of a point  
n: number of clusters you want  

```{r}
k_cluster = function(x, y, n){
  
  # Define distance function
  distance = function(point1, point2){
    a <- point1[1] - point2[1]
    b <- point1[2] - point2[2]
    ds <- (a ^ 2 + b ^ 2) ^ 0.5
    return(ds)
  }
  
  # Setup pointset
  pointset = cbind(x,y)
  
  for(it in 1:100){
    
    # Starting position of n points
    start <- rep(0, 2 * n)
    starting_points = matrix(data = start, nrow = n, ncol = 2)
    
    #give initial value
    
    for(i in 1:n){
      d <- quantile(x, (i-0.5)/n)
      e <- quantile(y, (i-0.5)/n)
      starting_points[i,] = c(d, e)
    }
    
    value <- rep(0, dim(pointset)[1] * n)
    dist_mat = matrix(data <- value, nrow = dim(pointset)[1], ncol = n)
    
    for(i in 1:n){
      dist_pi = vector()
      for(j in 1:dim(pointset)[1]){
        dist_pi = c(dist_pi, distance(pointset[j,], starting_points[i,]))
      }
      dist_mat[,i] = dist_pi
    }
    
    which_group = vector()
    for(i in 1:dim(pointset)[1]){
      which_group[i] = which.min(dist_mat[i,])
    }
    
    for(i in 1:n){
      one_group = pointset[which_group == i,]
      if(length(one_group) > 0){
        starting_points[i,] = c(mean(one_group[,1]), mean(one_group[,2]))
      }
    }
    
  }
  
    
    plot(x, y, col = which_group + 1, xlab = deparse(substitute(x)), ylab = deparse(substitute(y)), pch = 16)
    
    # Plot out centers
    for(i in 1:n){
      points(starting_points[i,1], starting_points[i,2], cex = 2.5, col = i + 1, pch = 8)
    }
    
  return(which_group)
}
```

and you can simply use it with \code{k_cluster(x, y, n)}, for example:

```{r}
k_cluster(cars$dist, cars$speed, 3)
```

the first output presents the belonged cluster number of each point and the figure illustrate n clusters using different colors and n clusters' center use stars.